---
title: "Homework 3"
author: "Mari Sanders"
date: "2024-10-12"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
library(tidyverse)
data("birthwt")
```

# Problem 1 

a) 

```{r}
x <- 
  birthwt %>% 
  pull(lwt)

t.test(x, conf.level = 0.95)
```

b)

We are 95% confident that the true  average weight of American Women is between 125.4270 and 134.2027 pounds. 
c) 

Since 171 is not in our confidence interval, we can reject the hypothesis that the average weight of American women is 171 pounds. 

# Problem 2 

a) 

```{r}
not_smoke <- 
  birthwt %>% select(lwt, smoke) %>% filter(smoke == 0) %>% select(-smoke) %>% pull(lwt)

smoke <- 
  birthwt %>% select(lwt, smoke) %>% filter(smoke == 1) %>% select(-smoke) %>% pull(lwt)

var.test(not_smoke, smoke, alternative = "two.sided", conf.level = 0.95)
```

b) 

We should preform a two sample t test with variance, since we get that the p-value is 0.09 we fail to reject the null hypothesis that the variances are equal. 

c) 

```{r}
t.test(not_smoke, smoke, var.equal = TRUE, conf.level = 0.90)
```

We get a p-value to be 0.5161. This means we fail to reject the null hypothesis that 

# Problem 3 

a) 

```{r}
hypertension <- 
  birthwt %>% pull(ht)
t.test(hypertension, conf.level = 0.99, alternative = c("two.sided"))
```

We are 99% confident that the true value of Amreican women that suffer from hypertension is between 0.0172132 and 0.1097709. 

Since the p-value is 0.0004 and the confidence interval does not include 0.2, we can reject the null hypothesis that the 20% of American women suffer from hypertension. 

b) 

```{r}
#prop.test(hypertension, alternative = "less", conf.level = )
```

# Problem 4 

```{r}

```

# Problem 5 

a) An ANOVA test would be the most appropriate because `race` is has more than two groups and `bwt` is continuous. 

b) 
k > 2, independence, normality, variances are the same 
```{r}

```

